15th International Satisfiability Modulo Theories Competition (SMT-COMP 2021): Rules and Procedures

### 2021-05-07 rules/rules21.tex
updating model validation track with new divisions

  \rationale{There were only small issues with last year's divisions, so there is no
    reason to keep them experimental. For the new divisions, as before, given the
    inconsistencies across different model producing solvers, we proceed in an
    experimental fashion to push for model standardization.}

@@

\header{Benchmark Selection.}
This track has the divisions
QF\_BV, QF\_IDL, QF\_RDL, QF\_LIA, QF\_LRA, QF\_LIRA,
QF\_UFIDL, QF\_UFLIA, and QF\_UFLRA.
%
This year all UF logics (with uninterpreted functions) are experimental divisions.
%
It will run on a
selection of non-incremental benchmarks with status \texttt{sat} from these
logics (as described on page~\pageref{benchmark-selection}).

>>>>

  \rationale{There were only small issues with last year's divisions, so there
    is no reason to keep them experimental. For the new divisions, as before,
    given the inconsistencies across different model producing solvers, we
    proceed in an experimental fashion to push for model standardization. Since
    both arrays and datatypes add further complications on top of uninterpreted
    functions, we exclude benchmarks containing those.}

@@

\header{Benchmark Selection.}  This track has the divisions QF\_Bitvec,
QF\_LinearIntArith, QF\_LinearRealArith, QF\_Equality (only with QF\_UF
benchmarks), QF\_Equality+LinearArith (only with QF\_UFIDL, QF\_UFLIA, and
QF\_UFLRA benchmarks), and QF\_Equality+Bitvec (only with QF\_UFBV benchmarks).
%
This year all divisions with UF logics (with uninterpreted functions) are
experimental divisions.
%
The track will run on a
selection of non-incremental benchmarks with status \texttt{sat} from these
logics (as described on page~\pageref{benchmark-selection}).
%
We exclude from the selection all benchmarks containing arrays or datatypes.
